\documentclass[conference]{IEEEtran}

% -------------------- Packages --------------------
\usepackage{times}        % Times New Roman
\usepackage{mathptmx}     % Math font
\usepackage{cite}         % IEEE citation format
\usepackage{graphicx}     % Images
\usepackage{amsmath}      % Math
\usepackage{url}          % URL formatting
\usepackage{lipsum}       % Dummy text (optional)
\usepackage[colorlinks=false, pdfborder={0 0 0}]{hyperref}
     % Clickable links


% -------------------- Document --------------------
\begin{document}

\title{Solar-Powered Smart Irrigation System}

\author{ \IEEEauthorblockN{ \begin{tabular}{ccc} \small M. Sakib Rahman & \small Shahrier Alam Shimul & \small Salman Nur Ramim \\ \footnotesize Dept. of Computer Science and Engineering & \footnotesize Dept. of Computer Science and Engineering & \footnotesize Dept. of Computer Science and Engineering \\ \footnotesize University of Asia Pacific, Dhaka, Bangladesh & \footnotesize University of Asia Pacific, Dhaka, Bangladesh & \footnotesize University of Asia Pacific, Dhaka, Bangladesh \\ \footnotesize Email: 22201240@uap-bd.edu & \footnotesize Email: 22201227@uap-bd.edu & \footnotesize Email: 22201239@uap-bd.edu \end{tabular} } } \maketitle

% -------------------- Sections --------------------
\input{Abstract.tex}
\vspace{0.5em}

\input{Keywords.tex}
\vspace{0.5em}

\input{Introduction.tex}
\vspace{0.5em}

\input{System_Design_&_Methodology.tex}
\vspace{0.5em}

\input{Implementation_and_Results.tex}
\vspace{0.5em}

\input{Conclusion.tex}
\vspace{0.5em}


% -------------------- References --------------------
\begin{thebibliography}{99}

\bibitem{electronicsworkshops21}
“Smart Irrigation System Using Dual Axis Solar Tracker,” Electronics Workshops, May 19, 2021. 
Available: \url{https://electronicsworkshops.com/smart-irrigation-system-using-dual-axis-solar-tracker/}. 
Accessed: Oct. 23, 2025.

\bibitem{youtubeSmartIrrigation21}
“Smart Irrigation System Using Dual Axis Solar Tracker,” YouTube video, 2021. 
Available: \url{https://www.youtube.com/watch?v=wIzwv6LcriA&t=330s}. 
Accessed: Oct. 23, 2025.

\bibitem{ScienceDirect2022}
K. Obaideen, B. A. A. Yousef, M. N. AlMallahi, Y. C. Tan, 
M. Mahmoud, H. Jaber, and M. Ramadan, 
“An overview of smart irrigation systems using IoT,” 
\textit{Energy Nexus}, vol. 7, Art. no. 100124, 2022. 
Available: \url{https://www.sciencedirect.com/science/article/pii/S2772427122000791}. 
Accessed: Oct. 23, 2025.

\bibitem{IRJET2018}
S. B. Pawar, P. Rajput and A. Shaikh, “Smart Irrigation System Using IoT and Raspberry Pi,” 
*International Research Journal of Engineering and Technology (IRJET)*, vol. 5, no. 8, pp. 1160–1165, Aug. 2018.  
Available: \url{https://www.academia.edu/download/57400791/IRJET-V5I8197.pdf}. 
Accessed: Oct. 23, 2025.

\bibitem{MDPI2020}
L. García, L. Parra, J. M. Jiménez, J. Lloret and P. Lorenz, 
“IoT-Based Smart Irrigation Systems: An Overview on the Recent Trends on Sensors and IoT Systems for Irrigation in Precision Agriculture,” 
*Sensors*, vol. 20, no. 4, Article 1042, Feb. 2020.  
Available: \url{https://www.mdpi.com/1424-8220/20/4/1042}. 
Accessed: Oct. 23, 2025.

\end{thebibliography}

\end{document}
